---
title: "Simulationsstudie"
output: html_document
---
Authors: Sven Lütke-Bordewick, Luisa Schuhmann , Kim Schäffner


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(parallel)
library(pacman)
p_load(VIM)
p_load(mice)
p_load(MASS)
p_load(dplyr)
p_load(smcfcs)
p_load(tidyverse)
p_load(pbapply)
p_load(mitools)
```





#Generate the testdata

```{r}
generate_testdata <- function(n_obs, 
                              missing_mechanism,
                              # mechanism of missing obs_data
                              seed = NULL,
                              missing){
  if (is.null(seed)) {
    seed <- sys.time()
    }
  
  set.seed(seed)
  
  x1 <- rnorm(n_obs, 2, 1)
  x_sqrd <- x1^2
  x2 <- x1 + rnorm(n_obs, 0, 3)
  y <-  4 * x1 + x_sqrd + 2 * x2 + rnorm(n_obs, 0, 10)
  
  obs_data <-  data.frame(y, x_sqrd, x1,x2)
  
  # delete observations depending on the mechanism
  missing_data <- switch(
    missing_mechanism,
    "MCAR" = mcar(obs_data, missing, c("x1", "x_sqrd")),
    "MAR"  = mar(obs_data, missing, c("x1", "x_sqrd"), "x2")
  )
      
    list(obs_data, missing_data, inputs = c(n_obs, 
                              missing_mechanism,
                              missing))  
  
}

mcar <- function(obs_data, missing, missing_var) {
  output <- obs_data
  output[sample(1:nrow(obs_data), size = nrow(obs_data) * missing),
         missing_var] <- NA
  output
}

mar <- function(obs_data, missing, missing_var, ctrl_var) {
  # model missingness via linear regression model
  # depending on 'ctrl_var' and random error
  output <- obs_data
  mis_mar <-
    0.5 + 2 * obs_data[, ctrl_var] +
    rnorm(nrow(obs_data), 0, 3)
  mis_index <- mis_mar < quantile(mis_mar, missing)
  output[mis_index, missing_var] <- NA
  output
}
```

# Generate Testdata with Interaction

```{r}
generate_testdata_interaktion <- function(n_obs, 
                              missing_mechanism,
                              # mechanism of missing obs_data
                              seed = NULL,
                              missing){
  if (is.null(seed)) {
    seed <- sys.time()
    }
  
  set.seed(seed)
  
  x1 <- rnorm(n_obs, 2, 1)
  x2 <- rnorm(n_obs, 2, 1)
  x3 <- x1 + rnorm(n_obs, 0, 3)
  y <-  2*x1 + 3*x2  + 2 * x3 + 2 * x1*x2 + rnorm(n_obs, 0, 10)
  
  obs_data <-  data.frame(y, x1, x2,x3)
  
  # delete observations depending on the mechanism
  missing_data <- switch(
    missing_mechanism,
    "MCAR" = mcar(obs_data, missing, c("x1", "x2")),
    "MAR"  = mar(obs_data, missing, c("x1", "x2"), "x3")
  )
      
    list(obs_data, missing_data, inputs = c(n_obs, 
                              missing_mechanism,
                              missing))  
  
}
```

# Generate Testdata for Log-Normal Distributed X

```{r}
generate_testdata_log <- function(n_obs, 
                              missing_mechanism,
                              # mechanism of missing obs_data
                              seed = NULL,
                              missing){
  if (is.null(seed)) {
    seed <- sys.time()
    }
  
  set.seed(seed)
  
  x1 <- rlnorm(n_obs, log(2), log(2))
  x_sqrd <- x1^2
  x2 <- x1 + rnorm(n_obs, 0, 3)
  y <-  4 * x1 + x_sqrd + 2 * x2 + rnorm(n_obs, 0, 20)
  
  obs_data <-  data.frame(y, x_sqrd, x1,x2)
  
  # delete observations depending on the mechanism
  missing_data <- switch(
    missing_mechanism,
    "MCAR" = mcar(obs_data, missing, c("x1", "x_sqrd")),
    "MAR"  = mar(obs_data, missing, c("x1", "x_sqrd"), "x2")
  )
      
    list(obs_data, missing_data, inputs = c(n_obs, 
                              missing_mechanism,
                              missing))  
  
}
```




#Test design

```{r}
test_design <- expand.grid(c(300L, 1000L), # number of observartions
                           c("MCAR", "MAR"),
                           c(0.1, 0.3, 0.5),
                           c(1:1000), stringsAsFactors = FALSE) # seeds for datageneration

names(test_design) <- c("n_obs", "missing_mechanism", "missing", "seed")

test_design %>% head(n = 12)





```

# Apply the design to generate data

```{r}

#Generate 1000 different datasets for each case with x^2



datasets <-
  test_design %>%
  pbapply(MARGIN = 1,
    function(x){ generate_testdata(n_obs = as.integer(x["n_obs"]),
      missing_mechanism = as.character(x["missing_mechanism"]),
      seed = as.integer(x["seed"]),
      missing = as.numeric(x["missing"])
      )})






#data_sets_all <-  datasets
#datasets <- data_sets_all[1:12]



# do the same for data with interaction
datasets_interaktion <-
  test_design %>%
  pbapply(MARGIN = 1,
    function(x){ generate_testdata_interaktion(n_obs = as.integer(x["n_obs"]),
      missing_mechanism = as.character(x["missing_mechanism"]),
      seed = as.integer(x["seed"]),
      missing = as.numeric(x["missing"])
      )})



# gerade data for log normal

datasets_log <-
  test_design %>%
  pbapply(MARGIN = 1,
    function(x){ generate_testdata_log(n_obs = as.integer(x["n_obs"]),
      missing_mechanism = as.character(x["missing_mechanism"]),
      seed = as.integer(x["seed"]),
      missing = as.numeric(x["missing"])
      )})


```

# Missing Data

Check the missing data pattern

```{r}
# data with x^2

for(i in 1:length(datasets)){
  marginplot(datasets[[i]][[2]][, c("x1","y")])
             }

# data with interaction:

for(i in 1:12){
  marginplot(datasets_interaktion[[i]][[2]][, c("x1","y")])
             }

# what is the r^2 for x^2:

output <- lm("y ~ x1 +x2 + x_sqrd", data = datasets[[3]][[1]])

summary(output)


# what is the r^2 for log:

output <- lm("y ~ x1 +x2 + x_sqrd", data = datasets_log[[3]][[1]])

summary(output)

```







# SMCFCS

```{r}

# X Squared

cl <- makeCluster(10)

# Parallel:

clusterEvalQ(cl, library(smcfcs))

system.time(imputated_data_set <- parLapply(cl, datasets, function(x){
  mis_data <- x[[2]]
  
  
  imputations <- smcfcs(mis_data, smtype = "lm", smformula = "y ~ x1 + x2 + x_sqrd", method =c("", "x1^2", "norm", ""), 
                        rjlimit = 3000)
}))


stopCluster(cl)


# save imputed data from first set

# saveRDS(imputated_data_set, "imputed_data_x_squared.rds")


## For interaction

cl <- makeCluster(10)

# Parallel:

clusterEvalQ(cl, library(smcfcs))

system.time(imputated_data_set_interaktion <- parLapply(cl, datasets_interaktion, function(x){
  mis_data <- x[[2]]
  
  
  imputations <- smcfcs(mis_data, smtype = "lm", smformula = "y ~ x1 + x2 + x1*x2 + x3 ", method =c("", "norm", "norm", ""), 
                        rjlimit = 3000)
}))


stopCluster(cl)


# For log Distribution

cl <- makeCluster(10)

# Parallel:

clusterEvalQ(cl, library(smcfcs))

system.time(imputated_data_set_log <- parLapply(cl, datasets_log, function(x){
  mis_data <- x[[2]]
  
  
  imputations <- smcfcs(mis_data, smtype = "lm", smformula = "y ~ x1 + x2 + x_sqrd", method =c("", "x1^2", "norm", ""), 
                        rjlimit = 3000)
}))


stopCluster(cl)



```

# Test if default number of iterations is fine

```{r}
# nomral data

cl <- makeCluster(10)


datasets_iteration <- datasets[1:12] # test iterations for each type of data

clusterEvalQ(cl, library(smcfcs))

system.time(imputated_data_set_iteration <- parLapply(cl, datasets_iteration, function(x){
  mis_data <- x[[2]]
  
  
  imputations <- smcfcs(mis_data, smtype = "lm", smformula = "y ~ x1 + x2 + x_sqrd", method =c("", "x1^2", "norm", ""), 
                        rjlimit = 3000, numit = 100)
}))



lapply(imputated_data_set_iteration, plot) # plot the data to see when there is convergence (should be before the default of 10 iterations otherwise we need more)

# For Log normal data


datasets_iteration <- datasets_log[1:12] # test iterations for each type of data

clusterEvalQ(cl, library(smcfcs))

system.time(imputated_data_set_iteration_log <- parLapply(cl, datasets_iteration, function(x){
  mis_data <- x[[2]]
  
  
  imputations <- smcfcs(mis_data, smtype = "lm", smformula = "y ~ x1 + x2 + x_sqrd", method =c("", "x1^2", "norm", ""), 
                        rjlimit = 3000, numit = 100)
}))

lapply(imputated_data_set_iteration_log, plot)


# For interaktion data


datasets_iteration <- datasets_interaktion[1:12] # test iterations for each type of data

clusterEvalQ(cl, library(smcfcs))

system.time(imputated_data_set_iteration_interaktion <- parLapply(cl, datasets_iteration, function(x){
  mis_data <- x[[2]]
  
  
  imputations <- smcfcs(mis_data, smtype = "lm", smformula = "y ~ x1 + x2 + x_sqrd", method =c("", "x1^2", "norm", ""), 
                        rjlimit = 3000, numit = 100)
}))

lapply(imputated_data_set_iteration_interaktion, plot)

```

# Rubins Rule to get Values

```{r}
# true parameter:

true_value <- c(0,4,2,1)

# Get Coverage of Imputed Dataset

for(i in 1:length(datasets)){
    impobj <- imputationList(imputated_data_set[[i]]$impDatasets) 
    models <- with(impobj, lm(y~x1+x2+x_sqrd))
    sum_model <- summary(MIcombine(models))
    coverage <- sum_model$`(lower` < true_value & true_value < sum_model$`upper)`    
    test_design[i,5] <- mean(coverage)
    
    # bias
    
    bias <- imputated_data_set[[i]]$impDatasets[[1]]$x1 - datasets[[i]][[1]]$x1
    
    test_design[i,6] <- mean(bias)
    
    CI_wide <- sum_model$`upper)` - sum_model$`(lower` 
    
    test_design[i,7] <- mean(CI_wide)
    
    print(i)
    }


# rename columns


colnames(test_design)<- c("n_obs","missing_mechanism", "missing", "seed", "coverage", "bias", "CI_width")
colnames(test_design)


# get coverage by mechanism, missing and n

diagnostics <- test_design %>% 
  group_by(n_obs, missing_mechanism, missing) %>% 
  summarise(coverage_rate = mean(coverage), bias = mean(bias), CI_width = mean(CI_width))


test_design_smcfcs_normal <- test_design


```


```{r}
# true parameter:

true_value <- c(0,4,2,1)

# Get Coverage of Imputed Dataset

for(i in 1:length(datasets_log)){
    impobj <- imputationList(imputated_data_set_log[[i]]$impDatasets) 
    models <- with(impobj, lm(y~x1+x2+x_sqrd))
    sum_model <- summary(MIcombine(models))
    coverage <- sum_model$`(lower` < true_value & true_value < sum_model$`upper)`    
    test_design[i,5] <- mean(coverage)
    
    # bias
    
    bias <- imputated_data_set_log[[i]]$impDatasets[[1]]$x1 - datasets_log[[i]][[1]]$x1
    
    test_design[i,6] <- mean(bias)
    CI_wide <- sum_model$`upper)` - sum_model$`(lower` 
    
    test_design[i,7] <- mean(CI_wide)
    
    print(i)
    }


# rename columns


colnames(test_design)<- c("n_obs","missing_mechanism", "missing", "seed", "coverage", "bias", "CI_width")
colnames(test_design)



# get coverage by mechanism, missing and n

diagnostics_log <- test_design %>% 
  group_by(n_obs, missing_mechanism, missing) %>% 
  summarise(coverage_rate = mean(coverage), bias = mean(bias), CI_width = mean(CI_width))


test_design_log <- test_design


```

```{r}
# Coverage with interaktion

# true parameter:

true_value <- c(0,2,3,2,2)

# Get Coverage of Imputed Dataset

for(i in 1:length(datasets_interaktion)){
    impobj <- imputationList(imputated_dataset_interaktion[[i]]$impDatasets) 
    models <- with(impobj, lm(y~x1+x2+x1*x2+x3))
    sum_model <- summary(MIcombine(models))
    coverage <- sum_model$`(lower` < true_value & true_value < sum_model$`upper)`    
    test_design[i,5] <- mean(coverage)
    
    
    bias <- imputated_dataset_interaktion[[i]]$impDatasets[[1]]$x1 - datasets_interaktion[[i]][[1]]$x1
    test_design[i,6] <- mean(bias)
    
    CI_wide <- sum_model$`upper)` - sum_model$`(lower` 
    
    test_design[i,7] <- mean(CI_wide)
      
    print(i)
}


# rename columns


colnames(test_design)<- c("n_obs","missing_mechanism", "missing", "seed", "coverage", "bias", "CI_width")
colnames(test_design)


# get coverage by mechanism, missing and n

diagnostics_interaktion <- test_design %>% 
  group_by(n_obs, missing_mechanism, missing) %>% 
  summarise(coverage_rate = mean(coverage), bias = mean(bias), CI_width = mean(CI_width))


test_design_interaktion <- test_design

```

# CART

```{r}


## normal data

cl <- makeCluster(10)

# Parallel:

clusterEvalQ(cl, library(mice))

system.time(imputated_data_set_cart <- parLapply(cl, datasets, function(x){
  mis_data <- x[[2]]
  
  
  imputations <- mice(mis_data, method = "cart")
}))

data_completet_dart <- lapply(imputated_data_set_cart, FUN = complete, action = "long", include = FALSE)

## data with log-normal

clusterEvalQ(cl, library(mice))

system.time(imputated_data_set_cart_log <- parLapply(cl, datasets_log, function(x){
  mis_data <- x[[2]]
  
  
  imputations <- mice(mis_data, method = "cart")
}))


# data with interaction

clusterEvalQ(cl, library(mice))

system.time(imputated_data_set_cart_interaktion <- parLapply(cl, datasets_interaktion, function(x){
  mis_data <- x[[2]]
  
  
  imputations <- mice(mis_data, method = "cart")
}))

stopCluster(cl)


```

# Diagnose Cart

```{r}
# CART normal:


true_value <- c(0,4,2,1)

for(i in 1:length(datasets)){
  imp <- imputated_data_set_cart[[i]]
  fit <- with(imp, lm(y ~ x1 + x2 + x_sqrd))
  tab <- summary(pool(fit), "all", conf.int = TRUE)
  lower <- tab$`2.5 %`
  higher <- tab$`97.5 %`
  
  coverage <- lower < true_value & true_value < higher
  test_design[i,5] <- mean(coverage)
  
   # bias
  
  data <- complete(imp, action = "long", include = FALSE)
  bias <- mean(data$x1) - mean(datasets[[i]][[1]]$x1)
  
  test_design[i,6] <- bias
  
  test_design[i,7] <- mean(higher - lower)
  
  print(i)
  }


# rename columns


colnames(test_design)<- c("n_obs","missing_mechanism", "missing", "seed", "coverage", "bias", "CI_width")
colnames(test_design)


# get coverage by mechanism, missing and n

diagnostics_cart <- test_design %>% 
  group_by(n_obs, missing_mechanism, missing) %>% 
  summarise(coverage_rate = mean(coverage), bias = mean(bias), CI_width = mean(CI_width))


test_design_cart <- test_design



# cart log-normal

true_value <- c(0,4,2,1)

for(i in 1:length(datasets_log)){
  imp <- imputated_data_set_cart_log[[i]]
  fit <- with(imp, lm(y ~ x1 + x2 + x_sqrd))
  tab <- summary(pool(fit), "all", conf.int = TRUE)
  lower <- tab$`2.5 %`
  higher <- tab$`97.5 %`
  
  coverage <- lower < true_value & true_value < higher
  test_design[i,5] <- mean(coverage)
  
  # bias
  
  data <- complete(imp, action = "long", include = FALSE)
  bias <- mean(data$x1) - mean(datasets_log[[i]][[1]]$x1)
  
  test_design[i,6] <- bias
  
  
  test_design[i,7] <- mean(higher - lower)
  
  
  print(i)
  }


# rename columns


colnames(test_design)<- c("n_obs","missing_mechanism", "missing", "seed", "coverage", "bias", "CI_width")
colnames(test_design)


diagnostics_cart_log <- test_design %>% 
  group_by(n_obs, missing_mechanism, missing) %>% 
  summarise(coverage_rate = mean(coverage), bias = mean(bias), CI_width = mean(CI_width))


test_design_log_cart <- test_design


# For interaktion

true_value <- c(0,2,3,2,2)

for(i in 1:length(datasets_interaktion)){
  imp <- imputated_data_set_interaktion_cart[[i]]
  fit <- with(imp, lm(y ~ x1 * x2 + x3))
  tab <- summary(pool(fit), "all", conf.int = TRUE)
  lower <- tab$`2.5 %`
  higher <- tab$`97.5 %`
  
  coverage <- lower < true_value & true_value < higher
  test_design[i,5] <- mean(coverage)
  
  
  data <- complete(imp, action = "long", include = FALSE)
  bias <- mean(data$x1) - mean(datasets_interaktion[[i]][[1]]$x1)
  
  test_design[i,6] <- bias
  
  test_design[i,7] <- mean(higher - lower)
  
  print(i)
  
  
  
  }


# rename columns


colnames(test_design)<- c("n_obs","missing_mechanism", "missing", "seed", "coverage", "bias", "CI_width")
colnames(test_design)


# get coverage by mechanism, missing and n

diagnostics_cart_interaktion <- test_design %>% 
  group_by(n_obs, missing_mechanism, missing) %>% 
  summarise(coverage_rate = mean(coverage), bias = mean(bias), CI_width = mean(CI_width))

test_design_cart_interaktion <- test_design



```

# ItT Approach (default method so pmm)


```{r}


# remove x_sqrd from missing dataset

datasets_ItT <- lapply(datasets,function(x){
  dataset <- x[[2]] %>% select(-x_sqrd)
  })

datasets_ItT_log <- lapply(datasets_log,function(x){
  dataset <- x[[2]] %>% select(-x_sqrd)
  })



#Impute the values

# data normal
cl <- makeCluster(10)

clusterEvalQ(cl, library(mice))

system.time(imputated_data_set_ItT <- parLapply(cl, datasets_ItT, function(x){
  imputations <- mice(x)
}))

stopCluster(cl)


# data log normal

clusterEvalQ(cl, library(mice))

system.time(imputated_data_set_ItT_log <- parLapply(cl, datasets_ItT_log, function(x){
  imputations <- mice(x)
}))


# Inpute for interaktion

clusterEvalQ(cl, library(mice))

system.time(imputated_data_set_ItT_interaktion <- parLapply(cl, datasets_interaktion, function(x){
  
  missing_data <- x[[2]]
  imputations <- mice(missing_data)
}))

stopCluster(cl)

```

#Diagnostics for ItT

```{r}

# normal data

true_value <- c(0,4,2,1)

for(i in 1:length(datasets_ItT)){
  imp <- imputated_data_set_ItT[[i]]
  fit <- with(imp, lm(y ~ x1 + x2 + I(x1^2)))
  tab <- summary(pool(fit), "all", conf.int = TRUE)
  lower <- tab$`2.5 %`
  higher <- tab$`97.5 %`
  
  coverage <- lower < true_value & true_value < higher
  test_design[i,5] <- mean(coverage)
  
  # bias
  
  data <- complete(imp, action = "long", include = FALSE)
  bias <- mean(data$x1) - mean(datasets[[i]][[1]]$x1)
  
  test_design[i,6] <- bias
  
  test_design[i,7] <- mean(higher - lower)
  
  print(i)
  }


# rename columns


colnames(test_design)<- c("n_obs","missing_mechanism", "missing", "seed", "coverage", "bias", "CI_width")
colnames(test_design)


# get coverage by mechanism, missing and n

diagnostics_ItT <- test_design %>% 
  group_by(n_obs, missing_mechanism, missing) %>% 
  summarise(coverage_rate = mean(coverage), bias = mean(bias), CI_width = mean(CI_width))

test_design_ItT <- test_design




# for log data

true_value <- c(0,4,2,1)

for(i in 1:length(datasets_ItT_log)){
  imp <- imputated_data_set_ItT_log[[i]]
  fit <- with(imp, lm(y ~ x1 + x2 + I(x1^2)))
  tab <- summary(pool(fit), "all", conf.int = TRUE)
  lower <- tab$`2.5 %`
  higher <- tab$`97.5 %`
  
  coverage <- lower < true_value & true_value < higher
  test_design[i,5] <- mean(coverage)
  
  # bias
  
  data <- complete(imp, action = "long", include = FALSE)
  bias <- mean(data$x1) - mean(datasets_log[[i]][[1]]$x1)
  
  test_design[i,6] <- bias
  test_design[i,7] <- mean(higher - lower)
  
  print(i)
  }



colnames(test_design)<- c("n_obs","missing_mechanism", "missing", "seed", "coverage", "bias", "CI_width")
colnames(test_design)


# get coverage by mechanism, missing and n

diagnostics_ItT_log <- test_design %>% 
  group_by(n_obs, missing_mechanism, missing) %>% 
  summarise(coverage_rate = mean(coverage), bias = mean(bias), CI_width = mean(CI_width))

test_design_ItT_log <- test_design




# for interaktion

true_value <- c(0,2,3,2,2)

for(i in 1:length(datasets_interaktion)){
  imp <- imputated_data_set_ItT_interaktion[[i]]
  fit <- with(imp, lm(y ~ x1 * x2 + x3))
  tab <- summary(pool(fit), "all", conf.int = TRUE)
  lower <- tab$`2.5 %`
  higher <- tab$`97.5 %`
  
  coverage <- lower < true_value & true_value < higher
  test_design[i,5] <- mean(coverage)
  
  # bias
  
  data <- complete(imp, action = "long", include = FALSE)
  bias <- mean(data$x1) - mean(datasets_interaktion[[i]][[1]]$x1)
  
  test_design[i,6] <- bias
  test_design[i,7] <- mean(higher - lower)
  
  print(i)
  }


# rename columns

colnames(test_design)<- c("n_obs","missing_mechanism", "missing", "seed", "coverage", "bias", "CI_width")
colnames(test_design)


# get coverage by mechanism, missing and n

diagnostics_ItT_interaktion <- test_design %>% 
  group_by(n_obs, missing_mechanism, missing) %>% 
  summarise(coverage_rate = mean(coverage), bias = mean(bias), CI_width = mean(CI_width))

test_design_ItT_interaktion <- test_design


```







# JAV Aproach

```{r}
#Impute the values

# data normal
cl <- makeCluster(10)

clusterEvalQ(cl, library(mice))

system.time(imputated_data_set_last <- parLapply(cl, datasets, function(x){
   missing_data <- x[[2]]
  imputations <- mice(missing_data)
}))


# Create the Variable X^2

# data log normal

clusterEvalQ(cl, library(mice))

system.time(imputated_data_set_last_log <- parLapply(cl, datasets_log, function(x){
  missing_data <- x[[2]]
  imputations <- mice(missing_data)
}))


# Inpute for interaktion

clusterEvalQ(cl, library(mice))

system.time(imputated_data_set_last_interaktion <- parLapply(cl, datasets_interaktion, function(x){
  
  missing_data <- x[[2]]
  imputations <- mice(missing_data)
}))

stopCluster(cl)


```

# Diagnostic JAV

```{r}


# JAV NORMAL

true_value <- c(0,4,2,1)

for(i in 1:length(datasets)){
  imp <- imputated_data_set_last[[i]]
  fit <- with(imp, lm(y ~ x1 + x2 + x_sqrd))
  tab <- summary(pool(fit), "all", conf.int = TRUE)
  lower <- tab$`2.5 %`
  higher <- tab$`97.5 %`
  
  coverage <- lower < true_value & true_value < higher
  test_design[i,5] <- mean(coverage)
  
  # bias
  
  data <- complete(imp, action = "long", include = FALSE)
  bias <- mean(data$x1) - mean(datasets[[i]][[1]]$x1)
  
  test_design[i,6] <- bias
  test_design[i,7] <- mean(higher - lower)
  
  print(i)
  }


# rename columns

# rename columns

colnames(test_design)<- c("n_obs","missing_mechanism", "missing", "seed", "coverage", "bias", "CI_width")
colnames(test_design)


# get coverage by mechanism, missing and n

diagnostics_JAV <- test_design %>% 
  group_by(n_obs, missing_mechanism, missing) %>% 
  summarise(coverage_rate = mean(coverage), bias = mean(bias), CI_width = mean(CI_width))

test_design_JAV <- test_design

# JAV LOG


true_value <- c(0,4,2,1)

for(i in 1:length(datasets_log)){
  imp <- imputated_data_set_last_log[[i]]
  fit <- with(imp, lm(y ~ x1 + x2 + x_sqrd))
  tab <- summary(pool(fit), "all", conf.int = TRUE)
  lower <- tab$`2.5 %`
  higher <- tab$`97.5 %`
  
  coverage <- lower < true_value & true_value < higher
  test_design[i,5] <- mean(coverage)
  
  # bias
  
  data <- complete(imp, action = "long", include = FALSE)
  bias <- mean(data$x1) - mean(datasets_log[[i]][[1]]$x1)
  
  test_design[i,6] <- bias
  test_design[i,7] <- mean(higher - lower)
  
  print(i)
  }


# rename columns


colnames(test_design)<- c("n_obs","missing_mechanism", "missing", "seed", "coverage", "bias", "CI_width")
colnames(test_design)


# get coverage by mechanism, missing and n

diagnostics_JAV_log <- test_design %>% 
  group_by(n_obs, missing_mechanism, missing) %>% 
  summarise(coverage_rate = mean(coverage), bias = mean(bias), CI_width = mean(CI_width))

test_design_JAV_log <- test_design




# for interaktion

true_value <- c(0,2,3,2,2)

for(i in 1:length(datasets_interaktion)){
  imp <- imputated_data_set_last_interaktion[[i]]
  fit <- with(imp, lm(y ~ x1*x2 + x3))
  tab <- summary(pool(fit), "all", conf.int = TRUE)
  lower <- tab$`2.5 %`
  higher <- tab$`97.5 %`
  
  coverage <- lower < true_value & true_value < higher
  test_design[i,5] <- mean(coverage)
  
  # bias
  
  data <- complete(imp, action = "long", include = FALSE)
  bias <- mean(data$x1) - mean(datasets_interaktion[[i]][[1]]$x1)
  
  test_design[i,6] <- bias
  test_design[i,7] <- mean(higher - lower)
  print(i)
  }


# rename columns


colnames(test_design)<- c("n_obs","missing_mechanism", "missing", "seed", "coverage", "bias", "CI_width")
colnames(test_design)


# get coverage by mechanism, missing and n

diagnostics_JAV_interaktion <- test_design %>% 
  group_by(n_obs, missing_mechanism, missing) %>% 
  summarise(coverage_rate = mean(coverage), bias = mean(bias), CI_width = mean(CI_width))

test_design_JAV_interaktion <- test_design



```


# Graphics

```{r}
# boxplot normal

dat1 <- test_design_smcfcs_normal %>% filter(missing_mechanism == "MAR" & n_obs == 1000 & missing != 0.3)
dat2 <- test_design_cart %>% filter(missing_mechanism == "MAR" & n_obs == 1000 & missing != 0.3)
dat3 <- test_design_JAV %>% filter(missing_mechanism == "MAR" & n_obs == 1000 & missing != 0.3)
dat4 <- test_design_ItT %>% filter(missing_mechanism == "MAR" & n_obs == 1000 & missing != 0.3)

dat1$method <- "SMC-FCS"
dat2$method <- "CART"
dat3$method <- "JAV"
dat4$method <- "ItT"

dat <- rbind(dat1,dat2,dat3,dat4)
dat$method <- factor(dat$method, c("SMC-FCS", "JAV", "ItT", "CART"))


dat %>% ggplot(aes(x = bias/2)) +
  geom_boxplot(aes(fill = method)) +
  facet_wrap(~ missing) +
  coord_flip() +
  labs(subtitle  = "Bias for different Method with n = 1000 and normal Distribution of x1", x = "relative Bias", title = "Model 1" ) +
  theme_bw()


# CI:



dat %>% ggplot(aes(x = CI_width)) +
  geom_boxplot(aes(fill = method)) +
  facet_wrap(~ missing) +
  coord_flip() +
  labs(subtitle  = "Bias for different Method with n = 1000 and normal Distribution of x1", x = "relative Bias", title = "Model 1" ) +
  theme_bw()





# boxplot log

dat1 <- test_design_log %>% filter(missing_mechanism == "MAR" & n_obs == 1000 & missing != 0.3)
dat2 <- test_design_log_cart %>% filter(missing_mechanism == "MAR" & n_obs == 1000 & missing != 0.3)
dat3 <- test_design_JAV_log %>% filter(missing_mechanism == "MAR" & n_obs == 1000 & missing  != 0.3)
dat4 <- test_design_ItT_log %>% filter(missing_mechanism == "MAR" & n_obs == 1000 & missing  != 0.3)

dat1$method <- "SMC-FCS"
dat2$method <- "CART"
dat3$method <- "JAV"
dat4$method <- "ItT"

dat <- rbind(dat1,dat2,dat3,dat4)
dat$method <- factor(dat$method, c("SMC-FCS", "JAV", "ItT", "CART"))


dat %>% ggplot(aes(x = bias/2)) +
  geom_boxplot(aes(fill = method)) +
  facet_wrap(~ missing) +
  coord_flip() +
  labs(subtitle  = "Bias for different Method with n = 1000 and x1 Log-Normal Distributed", x = "relative Bias", title = "Model 1" ) +
  theme_bw()



# CI:


dat %>% ggplot(aes(x = CI_width)) +
  geom_boxplot(aes(fill = method)) +
  facet_wrap(~ missing) +
  coord_flip() +
  labs(subtitle  = "Bias for different Method with n = 1000 and normal Distribution of x1", x = "relative Bias", title = "Model 1" ) +
  theme_bw()

# boxplot interaktion

dat1 <- test_design_interaktion %>% filter(missing_mechanism == "MAR" & n_obs == 1000 & missing != 0.3)
dat2 <- test_design_cart_interaktion %>% filter(missing_mechanism == "MAR" & n_obs == 1000 & missing != 0.3)
dat3 <- test_design_JAV_interaktion %>% filter(missing_mechanism == "MAR" & n_obs == 1000 & missing != 0.3)
dat4 <- test_design_ItT_interaktion %>% filter(missing_mechanism == "MAR" & n_obs == 1000 & missing != 0.3)

dat1$method <- "SMC-FCS"
dat2$method <- "CART"
dat3$method <- "JAV"
dat4$method <- "ItT"

dat <- rbind(dat1,dat2,dat3,dat4)
dat$method <- factor(dat$method, c("SMC-FCS", "JAV", "ItT", "CART"))

dat %>% 
  ggplot(aes(x = bias/2)) +
  geom_boxplot(aes(fill = method)) +
  facet_wrap(~ missing) +
  coord_flip() +
  labs(subtitle  = "Bias for different Method with n = 1000 and interaction between x1 and x2", x = "relative Bias", title = "Model 2" ) +
  theme_bw()

dat %>% ggplot(aes(x = CI_width)) +
  geom_boxplot(aes(fill = method)) +
  facet_wrap(~ missing) +
  coord_flip() +
  labs(subtitle  = "Bias for different Method with n = 1000 and normal Distribution of x1", x = "relative Bias", title = "Model 1" ) +
  theme_bw()


```

